Binning Strategies and Related Loss for Binned Scatterplots of Large Data

### 2016-10-04 versionForJCGS/PaperJCGS.Rnw
edit on file conflict

<<setup4,echo=F,include=F,eval=T>>=

# library(dbData)
library(devtools)
library(ggplot2)
library(gridExtra)
library(hexbin)
library(Hmisc)
library(lubridate)
library(MASS)
library(plyr)
library(RColorBrewer)
library(reshape2)
library(scales)
library(tidyr)
library(xtable)
library(scagnostics)

@@

# Load all data: pitching and binning loss demo
load("./data/pitching.Rdata")
load("./data/BinningLossDemos.Rdata")
@

@@

# # Hex binned scatterplot
#   qplot(data=pitchdat, x=G, y=SO, geom="hex", fill=..count.., group=1) +  
#   scale_fill_gradient("Frequency", low="#56B1F7", high="#132B43", guide="legend", trans="log", breaks=c(1, 10, 100, 1000)) + theme_bw() + xlab("Games (Count)") + ylab("Strike Outs (Count)") + theme(legend.position="bottom")
#   ggsave("./figure/HexBinning.png", width=5, height=5, dpi=300)
d1.hex.obj <- hexbin(pitchdat$G, pitchdat$SO)
d1.hex <- data.frame(hcell2xy(d1.hex.obj))
names(d1.hex) <- c("G", "SO")
d1.hex$Freq <-  d1.hex.obj@count

# hex binned bubbleplot
qplot(data=d1.hex, x=G, y=SO, geom="point", size=Freq+1) + 
  scale_size_area("Frequency", max_size=4, trans="log", breaks=c(1, 10, 100, 1000, 10000))+ theme_bw() + xlab("Games (Count)")+ ylab("Strike Outs (Count)") + theme(legend.position="bottom")
ggsave("./figure/BinBubble.png", width=5, height=5, dpi=300)

>>>>

<<setup4,echo=F,include=F,eval=T>>=
# library(dbData)
library(devtools)
library(ggplot2)
library(gridExtra)
library(hexbin)
library(Hmisc)
library(lubridate)
library(MASS)
library(plyr)
library(RColorBrewer)
library(reshape2)
library(scales)
library(tidyr)
library(xtable)
library(scagnostics)

@@

# Load all data: pitching and binning loss demo
load("./data/pitching.Rdata")
# load("./data/BinningLossDemos.Rdata")
@

@@

# Hex binned scatterplot
ggplot(data=pitchdat, aes(x=G, y=SO))+
    geom_hex()+
  scale_fill_gradient("Frequency", low="#56B1F7", high="#132B43", guide="legend", trans="log", breaks=c(1, 10, 100, 1000)) + theme_bw() + xlab("Games (Count)") + ylab("Strike Outs (Count)") + theme(legend.position="bottom")
  ggsave("./figure/HexBinning.png", width=5, height=5, dpi=300)
